### 2018-07-31 other_R_code/article_selection_process.Rnw
Further development of alogorithm description

With even a small number of search terms it quicly becomes impractical to examine all the documents even for a single day.

@@

Algorithm:
\begin{enumerate}
  \item use classifier on $R$ and $S$ to identify two lists of keywords
  \item generate probability from classifier parameters
  \item add to keyword list based on probability
\end{enumerate}

\end{document}

>>>>

With even a small number of search terms it quickly becomes impractical to examine all the documents even for a single day.

@@

Algorithm:
\begin{enumerate}
  \item use classifier on $R$ and $S$ to identify two lists of keywords
  \item generate probability from classifier parameters
  \item add to keyword list based on probability
\end{enumerate}
<<findkeywords>>=
keywords<-nb_keywords(classified_dfm, "EV_article")
knitr::kable(head(keywords, 20))
@

\section{Refinement Using Description}

<<usingdescription, warning=FALSE>>=
description_corpus<-quanteda::corpus(classdocs[,c("fakeid", "description", "EV_article")], text_field = "description")
description_dfm <- preprocess_corpus(description_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)

both_dfms<-split_dfm(description_dfm, n_train = 1000)

nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
res<-data.frame(predict_nb=pred_nb, prob_nb)
names(res)<-c("predict_nb", "prob_notev", "prob_ev")
assess_classification(organise_results(both_dfms$test, res)) %>%
  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
  kable()
@

Note: this way of creating the dfm does make dfms terms equal because one overall dfm is created and then it is subset. You can see below that the number of features in both dfms is the same:

<<equaldfms>>=
print(both_dfms$train)
print(both_dfms$test)
@

\section{Refinement Using OCR}

<<usingocr>>=
ocr_corpus<-quanteda::corpus(classdocs[,c("fakeid", "ocr", "EV_article")], text_field = "ocr")
ocr_dfm <- preprocess_corpus(ocr_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)

both_dfms<-split_dfm(ocr_dfm, n_train = 1000)
nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
res<-data.frame(predict_nb=pred_nb, prob_nb)
names(res)<-c("predict_nb", "prob_notev", "prob_ev")
assess_classification(organise_results(both_dfms$test, res)) %>%
  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
  kable()
@

\section{King Algorithm: implementation}

\subsection{Incrementally Define $R$ and $S$}
$R$ is our reference set. [King suggestions: could define $R$ based on one simple keyword search].
\subsubsection{Intermediate step}
Take keywords in $R$, $K_R$, ranked by simple statistic such as document frequency or frequency-inverse document frequency. User examines elements of $K_R$ apart from those used to define the set and chooses some keywords to define $Q_S$, which in turn generates a definition for $S$ so that we can run the rest of the algorithm.
The user can continue to add keywords from $K_R$ into the final desired query $Q_RT$.
This step also mitigates the issue of how to define a search set in large data sets that do not fit into memory all at once or may not even be able to be retrieved all at onece. is the BNA.

\subsection{Partition $S$ into $T$ and $S \backslash T$}

\subsection{Discovering Keywords to Classify Documents}

\subsection{Human Input and Human-Computer Iteration}
\end{document}
